The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-10-23 Manuscript_draft/Draft.Rmd
Q10 figure in the draft

# Appendix
![Posteriors of the scaling parameter, varying as a function of single plots](../Figures/Appendix/posteriors_boxplots_A.png){width=60%}

>>>>

# Appendix
![Posteriors of the scaling parameter, varying as a function of single plots](../Figures/posteriors_boxplots_q10.png){width=60%}

![Posteriors of the scaling parameter, varying as a function of single plots](../Figures/Appendix/posteriors_boxplots_A.png){width=60%}
